Practical Optional Types for Clojure

### 2015-10-16 metatheory.tex
It fits.

Our main lemma says if there is a defined reduction, then the propositions, object
and type are correct.
The metavariable \definedreduction{} ranges over \v{}, \errorvalv{} and \wrong{}.

@@

  {\soundnesslemmahypothesis}
  \begin{proof}
    By induction on the derivation of \opsem {\openv{}} {\e{}} {\a{}}.
    (Full proof given as lemma~\ref{appendix:lemma:soundness}).
  \end{proof}
\end{lemma}

We can now state our soundness theorem.

>>>>

We can now state our main lemma and soundness theorem.  The
metavariable \definedreduction{} ranges over \v{}, \errorvalv{} and
\wrong{}. Proofs are deferred to \ref{appendix:lemma:soundness}.

@@

  {\soundnesslemmahypothesis}
\end{lemma}
